Prefetching SPARQL query cacher

### 2016-07-29 dissertation/cache-proxy.tex
Some todos; mention that analysers are important
Make the big table in Appendix landscape
on cache maintenance

\begin{figure}[h!]
\begin{center}
\includegraphics{architecture.pdf}
\caption{Architectural overview. The proposed system is represented
  inside the box titled ``Proxy''. It interacts with a client, a
  Triple Patterns Fragments Server and a SPARQL Endpoint. The most
  important component is the query engine, which consists of a query
  planner and a query evaluator.}\label{fig:arch}
\end{center}
\end{figure}

@@

\subsection{Analysis for prefetching}\ref{sec:analpre}

@@

@@

\begin{table}
\caption{The modules that enable the query cache}\label{tab:modules}
\begin{tabular}{ | l | p{3cm} | l |}
  \hline
  Module & Authors & Github URL \\ \hline

@@

  \hline
\end{tabular}
\end{table}
\todo{make it fit. Rotate?}

>>>>

\begin{figure}[h!]
\begin{center}
\includegraphics{architecture.pdf}
\caption{Architectural overview. The proposed system is represented
  inside the box titled ``Proxy''. It interacts with a client, a
  Triple Patterns Fragments Server and a SPARQL Endpoint. The most
  important components are the query engine, which consists of a query
  planner and a query evaluator, and the analysers that find
  subqueries to cache.}\label{fig:arch}
\end{center}
\end{figure}

@@

\subsection{Analysis for prefetching}\label{sec:analpre}

@@

Cache maintenance, for example purging elements that are not useful or
has expired from the cache, is an orthogonal problem to the proposed
system. It is currently done straightforwardly in the User Agent
described in Appendix~\ref{sec:modules} which supports HTTP caching as
specified in RFC7234 \cite{rfc7234}, but further sophistication could
be added without modifications to the rest of the system.

@@

\begin{landscape}
\begin{table}
\caption{The modules that enable the query cache}\label{tab:modules}
\begin{tabular}{ | l | p{3cm} | l |}
  \hline
  Module & Authors & Github URL \\ \hline

@@

  \hline
\end{tabular}
\end{table}
\end{landscape}
